---
title: "AssignmentFourRMD"
author: "Keirra Kennedy"
date: "5/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment Four
#Titanic 

On April 10, 1912, there were a total of 2,240 individuals on board of the most famous shipwreck in the world, the titatic.  Due to there not being enough lifeboats available,more than half of the passengers died. The goal of this project is to determine the amount of known survivors in an observation of 887.

*italic* The data was retrieved from Kaggle and encyclopedia-titanica. 

*Item 1 
 The code that imported and saved my dataset in R
 Titanicship <- read.csv(file.choose(), header = T)
 
```{r titanicship}
summary(Titanicship)
```
 
#Dataset

*Item 1 
Survived: 1 for survived 0 for did not survive
PClass: Passenger class ranging 1-3
Name: Name of individuals
Sex: Male or Female
Age: Age range from 0-80
Sibilings.Spouses.Abroad: If the individual had a sibiling or spouse on the ship
Parent.Children.Aboard: If the individual had a parent or child.
Fare: Ranged from $0-$512.33

#Dataprep

The data was prepared by omitting all nule variables. The variable list was condensed so that Pclass, Sibilings.Spouses.Abroad, Parent.Children.Aboard, were not present. 

#summary Statistics



```{r titanicship}
summary(Titanicship)
```

## Including Plots
*Item 1
The plot below describes th survival rate of diffferent age groups.


```{r df, echo=FALSE}
plot(titans)
```

```{r df, echo=FALSE}
hist(df$Age)
```

*Item 2
The histogram give an idea of the frequency of age. 


